% TeX file: 5 Discussion of Results
\par \indent The general purpose for the general linear model is to identify 
the activated regions. From the figures of t values for each condition for one 
subject, the red regions are very likely to be the location of activation. 
We cannot name the regions since we do not have professional neuroscience 
background. However, since the topic of this project is about loss aversion 
and decision-making, we know that the core region corresponding to the 
decision-making and risk is ventral striatum. We particularly observed these 
regions. The ventral striatum is located near the center of the brain. From 
the plots of t-values on glass brains across 16 subjects, we can see that the 
color of the center is indeed red compared with yellow regions of other parts. 
The activated regions for both gain and loss task are very similar. It may 
reflect that the regions corresponding to these two tasks are very similar. 
However, connecting with the parameter maps for gain and loss, the regions are 
positively activated while facing gain task and the regions are negatively 
activated when facing loss task. From the color of the parameter maps across 16 
subjects, the brain seems more sensitive to the loss because the beta estimates 
at the activated regions are about -0.8. In the parameter maps for gain, the 
beta estimates at the activated regions are about 0.6. This finding somehow 
confirms with the conclusion of the project paper that people are more 
sensitive to loss than gain. However, the results from the plots are not 
accurate enough.


\par \indent After running a for loop for all 16 subjects that each has three
runs, we obtain a crude ovservation that the estimated coefficient in front of
the difference from indifference term vary braodly. We manually look at the 
results for each run and conclude the following observations: 
First, the p values for all 48 result text files showing the gain/loss term
are always presented in the proposed models with significant estimated 
coefficients. Second, the intercept terms are not always insignificant for 
different subjects. For all the gain/loss combination in run001, we find out 
that Subject 1, 2, 8, 13, 15 appear to be a loss-aversion person (the 
coefficient of difference from indifference is negative, meaning strong 
preference of rejecting the offer). Subject 6, 12, 14, 16 appear to be the 
more risk-like. 
Noticeably, the p value we are looking at are p values based on each person of
each run, thus lacking of a Bonderroni correction for doing multiple hypothesis 
testing.  

\par \indent In addition, by conjunction analysis, we analyze the relationship 
between behavioral loss aversion and neural loss aversion, which is core part 
in this research project. By observing the plots for correspondence of these 
two type of loss aversion, we can realize that the linear relationship between 
two is not very clear. We can see a general linear trend but not a perfect 
linear relationship. The robust regression identifies many outliers, which also 
suggests that they do not have a perfect linear relationship. However, one 
possible reason is that there are too few observations. So, if we would like to 
explore the relationship between these two types of loss aversion further, we 
must need to have enough observations.

